SDG contributions

### 2023-11-04 article/article.qmd
inspect top contributing institutions

>>>>

# Top institutions per SDG
```{r}
check_top_affils <- papers %>% 
  select(paperid, SDG_label, year, citations_norm) %>% 
  left_join(author_paper_affiliations_w_groups) %>% 
  left_join(affils) %>% 
  group_by(SDG_label, displayname, rank) %>% 
  summarise(n = n()) %>% 
  arrange(SDG_label, desc(n)) %>% 
  collect()
```

Interactively comparing institutions shows that there is specialisation across
the three SDGs: certain institutions (e.g. Mayo Clinic) publish a lot in one
SDG (here: SDG 3), but much less in others.
